The Unintended Consequences of Energy Reduction

### 2024-02-15 paper/paper.qmd
Reverted some changes from previous commit

![Relative Energy Consumption and Price](../other/figures/figure1.png){#fig-energy}

![Mortality Rate and Policy](../other/figures/figure3.png){#fig-mortality}

![Number of Heatstroke Incidents from 2008 to 2015](../other/figures/figure4.png){#fig-heatstrokeIncidents}

>>>>

![Figure 1](../other/figures/figure1.png)
![Figure 3](../other/figures/figure3.png)
![Figure 4](../other/figures/figure4.png)
